### 2025-04-05 correlation.qmd
20250405 - updates

An interactive visualization by @Magnusson2020 on interpreting correlations is at the following link: <https://rpsychologist.com/correlation/> (archived at <https://perma.cc/G8YR-VCM4>)

@@

A nonlinear correlation can be estimated using the $\xi$ coefficient from the `XICOR` package [@R-XICOR; @Chatterjee2023_packages]:

>>>>

An interactive visualization by @Magnusson2023 on interpreting correlations is at the following link: <https://rpsychologist.com/correlation/> (archived at <https://perma.cc/G8YR-VCM4>)

@@

A nonlinear correlation can be estimated using the xi ($\xi$) coefficient from the `XICOR` package [@R-XICOR; @Chatterjee2023_packages]:

### 2025-04-05 getting-started.qmd
20250405 - edits
20250405 - updates

Below is a visual that depicts various types of merges/joins.
Object `x` is the circle labeled as `x`.
Object `y` is the circle labeled as `y`.
The area of overlap in the Venn diagram indicates the rows on the keys that are shared between the two objects (e.g., the same `player_id`, `season`, and `week`).
The non-overlapping area indicates the rows on the keys that are unique to each object.
The shaded blue area indicates which rows (on the keys) are kept in the merged object from each of the two objects, when using each of the merge types.
For instance, a left outer join keeps the shared rows and the rows that are unique to object `x`, but it drops the rows that are unique to object `y`.

![Types of merges/joins](images/joinTypes.png)\

@@

At the end of each chapter in which `R` code is used, I provide the session information, which describes the system and operating system the code was run on and the versions of each package.
That way, if you get different results from me, you can see which differ, to help with reproducibility.
If you run the (all of) the exact same code as is provided in the text, in the exact same order, with the exact same setup (platform, operating system, package versions, etc.), you should get the exact same answer as is in the text.
That is the idea of reproducibility—getting the exact same result with the exact same inputs.
Reproducibility is crucial for studies to achieve greater confidence in their findings and to ensure better replicability of findings across studies.

>>>>

@fig-joinTypes depicts various types of merges/joins.
Object `x` is the circle labeled as `x`.
Object `y` is the circle labeled as `y`.
The area of overlap in the Venn diagram indicates the rows on the keys that are shared between the two objects (e.g., the same `player_id`, `season`, and `week`).
The non-overlapping area indicates the rows on the keys that are unique to each object.
The shaded blue area indicates which rows (on the keys) are kept in the merged object from each of the two objects, when using each of the merge types.
For instance, a left outer join keeps the shared rows and the rows that are unique to object `x`, but it drops the rows that are unique to object `y`.

::: {#fig-joinTypes}
![](images/joinTypes.png){width=100% fig-alt="Types of Merges/Joins."}

Types of Merges/Joins.
:::

@@

At the end of each chapter in which `R` code is used, I provide the session information, which describes the system and operating system the code was run on and the versions of each package.
That way, if you get different results from me, you can see which session settings differ, to help with reproducibility.
If you run the (all of) the exact same code as is provided in the text, in the exact same order, with the exact same setup (platform, operating system, package versions, etc.) and the exact same data, you should get the exact same answer as is in the text.
That is the idea of reproducibility—getting the exact same result with the exact same inputs.
Reproducibility is crucial for studies to achieve greater confidence in their findings and to ensure better replicability of findings across studies.
